\documentclass[PhD]{uclathes}

\input{preamble/preamble.tex}

\title{
  Search for New Heavy Resonances Decaying to $W$, $Z$, or Higgs Bosons and Upgrade of the Compact Muon Solenoid Level-1 Muon Trigger for the High Luminosity Large Hadron Collider
}

\author{David Warren Hamilton}
\department{Physics}
\degreeyear{2021}

\chair{Michail Bachtis}
\member{David Saltzberg}
\member{Jay Hauser}
%\member{Nathan Whitehorn}
\member{Thomas Dumitrescu}

\dedication{
  \textit{
    %(Dedication omitted for brevity.)
    To my parents, Gary and Elaine, for their endless love and support
  }
}

\acknowledgments{
  %(Acknowledgments omitted for brevity.)

  % Intro
  %Looking back on the last ten or so years, it is strange to think that this is where I ended up.
  %As a child, I grew up wanting to become a fighter pilot---and to some extent, that is still a career path that I've thought about pursuing.
  %Later on in high school, I started to become passionate about digital art, and I envisioned myself working as a developer in the video game industry.
  %However, I determined later on that this would not be a stable career path, and I ended up transferring to UT Austin as a physics major after spending a year and a half taking courses at community college.
  %My original intent during this time was to eventually transfer into electrical engineering, but having been denied an internal transfer request, %I ended up staying in physics and developing a passion for the subject, as well as picking up a mathematics degree along the way.
  %I also had the opportunity to participate in research as an undergrad, both at UT and through an internship at Brookhaven National Lab.
  %It was also during my undergraduate studies that I discovered a passion for tutoring, which is something that I still practice to this day.

  % Grad school

  % Advisor
  It is only fitting that I start by thanking my advisor, Michalis Bachtis, for his guidance and eagerness to take me on as a student after switching subfields during my third year.
  As an advisor, he has pushed me to become a better physicist, and has challenged me in ways that have contributed towards my growth during my studies.
  Having reflected on my time as his student, I believe that I have come out of it for the better, and I hope that being his first student to graduate has been as much of a fruitful learning experience for him as it has been for me.

  % Postdoc
  I would also like to thank our former postdoc, Simon Regnard, for his assistance throughout my graduate studies and his feedback on this work.
  There were many times over the last couple of years where he was more than willing to help me when I struggled during the course of my research.
  His guidance over the course of this project was invaluable, and I wish him the best of luck in his future endeavors outside of physics.

  % Fellow coworkers
  Beyond my advisor and postdoc, I would also like to thank our engineer Maxx Tepper, fellow students Tyler Lam, William Nash, and Brent Stone, as well as former student Christian Schnaible, for making the UCLA CMS group an enjoyable place to work.
  Two things I missed the most during the COVID-19 pandemic were our daily office shenanigans, and the fun conversations we'd have during lunch together.

  % Fellow students
  Since coming to UCLA, I have also made many friends that made living in Los Angeles an unforgettable experience.
  I would like to thank Lance Hildebrand, my friend and roommate, for all the enjoyable conversations we've had together, and for joining me in the mosh pit at many amazing metal shows.
  In addition to Lance, I'd also like to thank my friends and study buddies, Cole Stephens, Gurleen Bal, and Masha Sergeeva, for the summer we spent together preparing for our comprehensive exam.
  Many other friends I met during my time here are deserving of thanks as well, including Philip Lu, Warren Nadvornick, Matteo Vicino, John Gardiner, Stathis Megas, Teresa Le, Sarah Chase, Justin Faber, and Yeou Chiou.

  % Friends and family
  Beyond the friends I made here at UCLA, there are still many from my undergraduate experience at UT Austin that have supported me during their own graduate studies.
  In particular, I would like to thank Ruy Ibanez Amador, Paul Campbell, Alex Wilhelm, and Thanh Ha, for all the time spent together whenever I'd visit home, and for all our late night gaming sessions.
  I would also like to thank my childhood friend, Scott Wold, for keeping up with me all these years and being another reason to look forward to visiting Austin every year.
  Finally, I would like to thank my parents, Gary and Elaine, and my siblings, Laura and Matthew, for their love and support throughout my time in graduate school.
}

\vitaitem{2013-2015}
{
  Undergraduate Tutor,
  University of Texas,
  Austin, Texas
}

\vitaitem{2013-2015}
{
  Undergraduate Research Assistant,
  University of Texas
}

\vitaitem{2014}
{
  Undergraduate Research Intern,
  Brookhaven National Laboratory
}

\vitaitem{2015}
{
  B.S.\ (Physics) and B.S.\ (Mathematics),
  University of Texas
}

\vitaitem{2015-2017, 2020}
{
  Teaching Assistant,
  Department of Physics and Astronomy,
  UCLA,
  Los Angeles, California
}

\vitaitem{2017}
{
  M.S.\ (Physics),
  UCLA
}

\vitaitem{2017-2021}
{
  Graduate Research Assistant,
  Department of Physics and Astronomy,
  UCLA
}

\abstract{
  This thesis describes the search for a new heavy boson decaying to a pair of heavy electroweak bosons (\WW, \WZ, or \WH) in the semileptonic final state (electron or muon, missing transverse energy, and jet), using the data obtained from proton collisions in the Compact Muon Solenoid detector at the Large Hadron Collider.
  The data used, collected during the second run of the Large Hadron Collider, has integrated luminosities of $35.9\unit{fb^{-1}}$, $41.5\unit{fb^{-1}}$, and $59.7\unit{fb^{-1}}$ recorded for the years of 2016, 2017, and 2018, respectively.
  The analysis performed makes use of a novel two-dimensional signal extraction technique performed in the plane of the diboson invariant mass and jet mass, with the search performed in the resonance mass range from 1.0 to $4.5\unit{TeV}$.
  Results are obtained in terms of asymptotic exclusion limits, with no significant deviation from Standard Model predictions observed.
  We also present studies towards a novel muon tracking algorithm for the Level-1 Trigger of the Compact Muon Solenoid detector at the future High Luminosity Large Hadron Collider.
}

\begin{document}

\makeintropages

\input{chapters/introduction.tex}
\input{chapters/theory.tex}
\input{chapters/experiment.tex}
\input{chapters/analysis.tex}
\input{chapters/samples.tex}
\input{chapters/eventSelection.tex}
\input{chapters/controlPlots.tex}
\input{chapters/Vtag.tex}
\input{chapters/2Dfit.tex}
\input{chapters/uncertainties.tex}
\input{chapters/fitValidation.tex}
\input{chapters/results.tex}
\input{chapters/conclusion.tex}
\input{chapters/TPS.tex}

\bibliography{bib/articles,bib/books,bib/misc,bib/reports}
\bibliographystyle{unsrturl}

\end{document}
